\documentclass[../main.tex]{subfiles}

\begin{document}

\chapter{Language and Occupation}

\textbf{Why do jobs exist?}
\begin{itemize}
	\item money/economic development
	\item personal development/direction/self-worth
	\item survival (of?)
	\item domination (of global markets)
	\item contributions to society (what is an individual's role in society?)
	\item political administration of society (eg. USSR)
	\item societal function
\end{itemize}

\textbf{Are all jobs made equal?} How do we quantify value? How about in other countries? 
\exmp{Teaching}{Consider the different salaries of teachers in different countries: \begin{itemize}
		\item USA: \SI{50000}[\$]{}
		\item Luxembourg: \SI{110000}[\$]{}
		\item OECD Average: \SI{30000}[\$]{}
		\item Estonia: \SI{17000}[\$]{}
	\end{itemize}
This might say something about how these societies value teaching, and, by extension, education.
}

\exmp{Agriculture}{Agriculture is rather popular in Japan, but the enthusiasm might not be easily translated to Singapore.}

\section{Language in Occupations}
Language can be a way to measure societal attitudes towards a job, or as a way to access the job (and hence deny others access). There will be jobs that will be specialised and will have elements of language that need training and expertise. Hence, language becomes a differentiator in being qualified for a job.

\section{Industry-related Jargon}
Either specialised lexis or subject-specific terms, but intentionally coined within that industry/field. Some examples are medical terminology, legalese, and secret codes.

\exmp{Specialised Lexis}{\begin{itemize}
	\item In music, there are many loanwords from Italian, French, and German to describe music qualities (eg. \textit{forte}, \textit{crescendo}).
	\item In particle physics, words such as `spin', `charm', and `strange' are used to describe properties of particles.
	\item In soccer (also among managers and commentators), there is an interesting use of the present perfect tense in an interesting way: \begin{exe}
		\item he's gone past the defender and \underline{given} me a good pass, and I've knocked it in.
	\end{exe}
\end{itemize}}
\end{document}
